Catchy Part: Surveying Users' Perceptions of Threats for Wearable Devices

### 2014-12-20 wearables_survey.tex
added some appendixes and references.

\author{
% 1st. author
\alignauthor
Linda N. Lee\\
       \affaddr{UC Berkeley}\\
       \email{lnl@berkeley.edu}
% 2nd. author
\alignauthor
Serge Egelman\\
       \affaddr{UC Berkeley}\\
       \affaddr{ICSI}\\
       \email{serge@cs.berkeley.edu}
% 3rd. author
\alignauthor David Wagner\\
       \affaddr{UC Berkeley}\\
       \email{daw@cs.berkeley.edu}
}

@@

\section{Introduction}
Basically a longer version of the abstract, plus some additional motivational things thrown in here. I feel like I should have a couple sentences which lead into what I am going to talk about, or at least lead in with something catchy and strong. Hmm. Think about what to put here.

@@

\subsection{Validation}
(REDO) We conducted a focus group to look over the list, brainstorm more scenarios,  and get question feedback. We got a small sample of results (which were guided so we through them out, but it was helpful to know what we might expect) and clarify any scenarios which were unclear. Logistically, we also used this time to time the survey, made sure the survey worked, and other things. Quick demographics of the focus group here--(fix later) 12 people, X\% male, average age Y, with education ranging from A to B and professions including student, artist, business person, court judge, etc.

@@

\subsection{Format}
In total, the survey consisted of 367 unique questions, with each participant answering 27 questions. Out of the 27 seen by the participant, 10 of the questions are randomly selected from a particular set of questions (see below).   \\[-.8cm]

@@

To mitigate any biases, we randomized the order in which users saw groups of questions. That is; the participant has an equal chance of seeing questions related to threat perceptions or questions related to risk and benefit assessment of technologies. Additionally, each question in the sections about various scenarios, questions about smartphone scenarios, and IUIPC questions were randomly selected. A participant was also equally likely to see the risk or benefit questions first when they got to the section pertaining to risk and benefit assessment of technologies. (Ugh this is bad, re-write later)

\subsubsection{Threat Perceptions}
Before they get to the wearable device question, they must answer these two questions about the Cubetastic3000. people who did not answer these two comprehension questions were filtered out (this was about 4\% of our participants). These questions both filtered out people who were not paying attention, people who were rushing through it for money, etc.

@@

\subsubsection{Technology Perceptions}
The next set of questions are with respect to the Fischoff study on users’ perception of benefit and risk. We wanted to study personal but also broad perceptions of wearble risks. the We prompted the users with the same prompt that the participants in the Fischoff study was presented with, giving instructions to consider gross risk and gross benefits for a long period of time for all people, with specific instructions to numerical rankings. We did this so that we can calibrate the new technologies that we ask about with the existing seminal study. Prompt can be seen at <appendix something, add in soon>.

@@

\subsubsection{User Concerns}
Lastly, after investigating user perceptions of personal threats, general perceptions of risks and benefits, we thought we could just ask the users what they thought were the most likely risks.

@@

\subsubsection{Additional Questions}
During the exit portion of the survey, we asked for demographics (gender, age, education) along with if the person owns a wearable or not. We thought that would be important to know. Also, we imagined that privacy would be correlated to these results, which is why we made everyone take the IUIPC to see how much they cared about privacy. Explain why I used IUIPC instead of the Westin, just one or two sentences will do (cite the IUPIC paper, and the SOUPS paper on how the Westin is not so accurate).

@@

\subsubsection{Data Type}
blah blah here.

%For all recipients \\[-.8cm]
%
%\begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt
%  %\setcounter{enumi}{0}
%  \item a video of you unclothed
%  \item bank account information
%  \item social security number
%  \item video of you entering in your PIN
%  \item a photo of you unclothed
%  \item a photo of you that is incriminating or embarrassing
%  \item username and password for websites
%  \item credit card information
%  \item a video of you that is incriminating or embarassing
%  \item a photo you at home taken randomly by an inward-facing camera \\[-.8cm]
%\end{enumerate}
%
%\begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt
%  \setcounter{enumi}{63}
%  \item eye movement patterns (for eye tracking)
%  \item when and how much you exercise
%  \item when you are happy or having fun
%  \item which television shows you watch
%  \item when you are busy or interruptible
%  \item music from your device
%  \item your heart rate
%  \item your age 
%  \item the language you speak
%  \item your gender \\[-.8cm]
%\end{enumerate}

@@

\subsubsection{Data Recipient}

@@

\subsubsection{Risk and Benefit Ranks} 
\subsubsection{Lawnmower Ratios}

\subsection{Perceived Concerns for Wearable Devices}

Although we asked users about particular situations which might occur with a wearable device and asked them to assess technologies in a general sense, our open ended question asked the users to state the most likely risk(s) associated with owning and interacting with wearable devices. Without any doubt, the most common concern for owning and interacting with wearable devices for the every day user is the \textit{loss of privacy}.

Talk about the results of the open-ended answers here.

@@

%APPENDICES are optional
%\balancecolumns
\appendix
%Appendix A
\section{Full Survey}
\section{Detailed Situation Rankings}
\section{Detailed Tech Rankings}
\section{Focus Group Script}

>>>>

\author{
% 1st. author
\alignauthor
Linda N. Lee\\
       \affaddr{UC Berkeley}\\
       \email{lnl@cs.berkeley.edu}
% 2nd. author
\alignauthor
Serge Egelman\\
       \affaddr{UC Berkeley}\\
       \affaddr{ICSI}\\
       \email{serge@cs.berkeley.edu}
% 3rd. author
\alignauthor David Wagner\\
       \affaddr{UC Berkeley}\\
       \email{daw@cs.berkeley.edu}
}

@@

\section{Introduction}
(REDO) Basically a longer version of the abstract, plus some additional motivational things thrown in here. I feel like I should have a couple sentences which lead into what I am going to talk about, or at least lead in with something catchy and strong. Hmm. Think about what to put here.

@@

\subsection{Validation}
(REDO) We conducted a focus group to look over the list, brainstorm more scenarios,  and get question feedback. We got a small sample of results (which were guided so we through them out, but it was helpful to know what we might expect) and clarify any scenarios which were unclear. Logistically, we also used this time to time the survey, made sure the survey worked, and other things. Quick demographics of the focus group here--(fix later) 12 people, X\% male, average age Y, with education ranging from A to B and professions including student, artist, business person, court judge, etc.  You can look at the focus group script in appendix \ref{sec:script}.

@@

\subsection{Format}
(REDO) In total, the survey consisted of 367 unique questions, with each participant answering 27 questions. Out of the 27 seen by the participant, 10 of the questions are randomly selected from a particular set of questions (see below).   \\[-.8cm]

@@

To mitigate any biases, we randomized the order in which users saw groups of questions. That is; the participant has an equal chance of seeing questions related to threat perceptions or questions related to risk and benefit assessment of technologies. Additionally, each question in the sections about various scenarios, questions about smartphone scenarios, and IUIPC questions were randomly selected. A participant was also equally likely to see the risk or benefit questions first when they got to the section pertaining to risk and benefit assessment of technologies.

\subsubsection{Threat Perceptions}
(REDO) Before they get to the wearable device question, they must answer these two questions about the Cubetastic3000. people who did not answer these two comprehension questions were filtered out (this was about 4\% of our participants). These questions both filtered out people who were not paying attention, people who were rushing through it for money, etc.

@@

\subsubsection{Technology Perceptions}
(REDO) The next set of questions are with respect to the Fischoff study on users’ perception of benefit and risk. We wanted to study personal but also broad perceptions of wearble risks. the We prompted the users with the same prompt that the participants in the Fischoff study was presented with, giving instructions to consider gross risk and gross benefits for a long period of time for all people, with specific instructions to numerical rankings. We did this so that we can calibrate the new technologies that we ask about with the existing seminal study. Prompt can be seen at appendix \ref{sec:prompt}.

@@

\subsubsection{User Concerns}
(REDO) Lastly, after investigating user perceptions of personal threats, general perceptions of risks and benefits, we thought we could just ask the users what they thought were the most likely risks.

@@

\subsubsection{Additional Questions}
(REDO) During the exit portion of the survey, we asked for demographics (gender, age, education) along with if the person owns a wearable or not. We thought that would be important to know. Also, we imagined that privacy would be correlated to these results, which is why we made everyone take the IUIPC to see how much they cared about privacy. Explain why I used IUIPC instead of the Westin, just one or two sentences will do (cite the IUPIC paper, and the SOUPS paper on how the Westin is not so accurate).

@@

\subsubsection{Data Type}
(REDO)

For all recipients \\[-.8cm]

\begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt
  %\setcounter{enumi}{0}
  \item a video of you unclothed
  \item bank account information
  \item social security number
  \item video of you entering in your PIN
  \item a photo of you unclothed
  \item a photo of you that is incriminating or embarrassing
  \item username and password for websites
  \item credit card information
  \item a video of you that is incriminating or embarassing
  \item a photo you at home taken randomly by an inward-facing camera \\[-.8cm]
\end{enumerate}

\begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt
  \setcounter{enumi}{63}
  \item eye movement patterns (for eye tracking)
  \item when and how much you exercise
  \item when you are happy or having fun
  \item which television shows you watch
  \item when you are busy or interruptible
  \item music from your device
  \item your heart rate
  \item your age 
  \item the language you speak
  \item your gender \\[-.8cm]
\end{enumerate}

@@

\subsubsection{Data Recipient}
(REDO)

@@

\subsubsection{Risk and Benefit Ranks} 
(REDO)

\subsubsection{Lawnmower Ratios} 
(REDO)

\subsection{Perceived Concerns for Wearable Devices}
(REDO) Although we asked users about particular situations which might occur with a wearable device and asked them to assess technologies in a general sense, our open ended question asked the users to state the most likely risk(s) associated with owning and interacting with wearable devices. Without any doubt, the most common concern for owning and interacting with wearable devices for the every day user is the \textit{loss of privacy}.

(I should probably make a table of the following. Ugh, but for now:)

Privacy 				464 (25.99\%) \\
Security 				94 (5.27\%)\\
Hacking 				38 (2.13\%)\\
Spying 				50 (2.80\%)\\ [-.5cm]

Unaware Use 			167 (9.36\%)\\
Accidental Sharing 		66 (3.70\%)\\
Unaware Collection		64 (3.59\%)\\
Unaware Access	 	44 (2.46\%)\\
False Information 		33 (1.85\%)\\[-.5cm]

Health Risk 			252 (14.12\%)\\
Safety 				147 (8.24\%)\\
Financial Cost	 		201 (11.26\%)\\[-.5cm]

Social Impact 			135 (7.56\%)\\
Social Stigma 			39 (2.18\%)\\
Aesthetics 			19 (1.06\%)\\[-.5cm]

Miscellaneous 		76 (4.26\%)\\
None				51 (2.86\%)\\
Don't know			 30 (1.68\%)\\
Don't care 			6 (0.34\%)\\

Talk about the coding labels and what they mean, in a very vague and compact way. Refer people to the appendix \ref{sec:coding} for what the coding means in detail.

Takeaway is that people care about privacy, then security, health, social impact. Other interesting things to note are aesthetics, social stigma, and false information, which could be cool things to look into.

@@

%APPENDICES are optional
%\balancecolumns
\appendix
%Appendix A
\section{Focus Group Script}
\label{sec:script}

text text

\section{Fischoff Prompts}
\label{sec:prompt}

text text

\section{Coding Label Definitions}
\label{sec:coding}

text text
%\section{Detailed Tech Rankings}
